Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2014-10-01 exp1/present2013.tex
mention Empirical add TODOs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@760 43ef1190-90fd-4dd7-a769-d0121f02b80e
ISWC 2013 was a 20 minute talk Extending from here Details on the experiment
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@761 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

@@

@@

@@

  \begin{itemize}
  \item Code and instructions at Github:
    \url{https://github.com/kjetilk/doe-sparql}.
  \item Happy to help getting it to run!
  \item Happy to discuss collaborations or workshops on this topic!
  \end{itemize}

>>>>

% TODO: My factors

@@

\begin{itemize}
\item Just 2 levels.
\item Handful of illustrative factors.
\item Analysis that illustrates key concepts.
\item Straightforward to program and reproduce.
\item Artificial performance differences.
\end{itemize}

\begin{frame}{Choices to meet these constraints}

  \begin{itemize}
  \item Response variable: Time from DNS lookup finishes to endpoint
    has delivered a full response, measured by \texttt{curl}.
  \item We don't compare different implementions, we compare the
    performance before and after some change.
  \item Query engine: \texttt{4store} where we insert \textsf{sleep}
    statements in the join function on one level and language matching
    function on the other. 
  \end{itemize}

@@

% TODO: Much around the hypothesis test

@@

% Experimental economy

@@

  \begin{itemize}
  \item Code and instructions at Github:
    \url{https://github.com/kjetilk/doe-sparql}.
  \item Happy to help getting it to run!
  \item Happy to discuss collaborations!
  \item The ESWC Empirical workshop is a venue for this study: http://empirical-ws.org/
  \end{itemize}
